Upper Limits on CN from Falling Evaporating Bodies\\seen towards $\beta$~Pictoris

### 2025-02-08 src/tex/ms.tex
fix pdf section labels

\section{Searches for \ce{CN}}\label{sect:CNsearch}

@@

\subsection{Identifying exocomets from \ion{Ca}{ii} H line}\label{sect:FEBid}
The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
%
The deepest absorption feature in each observing night was selected, and the location and depth stored.
%
For the comet sample we selected features deeper than 60\% %\hl{and 40\%} for HARPS and UVES, respectively, 
while spectra with features below 15\% %for both HARPS and UVES 
were flagged as `low activity'.
%
The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}.

@@

\subsection{Cross-correlation with \ce{CN} models}\label{sect:CCF}

@@

\subsection{Estimating the \ce{CN} column density limits}\label{sect:CNlim}

@@

\subsection{1P/Halley at \bp{}}

@@

\subsection{Raising the \ce{CN} production rates}

>>>>

\section{Searches for \texorpdfstring{\ce{CN}}{CN}}\label{sect:CNsearch}

@@

\subsection{Identifying exocomets from \texorpdfstring{\ion{Ca}{ii}}{CaII} H line}\label{sect:FEBid}
The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
%
The deepest absorption feature in each observing night was selected, and the location and depth stored.
%
For the comet sample we selected features deeper than 60\% %\hl{and 40\%} for HARPS and UVES, respectively, 
while spectra with features below 15\% %for both HARPS and UVES 
were flagged as `low activity'.
%
The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}.

@@

\subsection{Cross-correlation with \texorpdfstring{\ce{CN}}{CN} models}\label{sect:CCF}

@@

\subsection{Estimating the \texorpdfstring{\ce{CN}}{CN} column density limits}\label{sect:CNlim}

@@

\subsection{1P/Halley at \texorpdfstring{\bp{}}{Beta Pictoris}}

@@

\subsection{Raising the \texorpdfstring{\ce{CN}}{CN} production rates}
